Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-18 revision-1/lang.tex
checkpoint

We let $x$ range over \emph{variables} which are
identifiers 
\begin{itemize}
  \item $S$ ranges over sets of 
\end{itemize}
We let $x$ range over variables.%, and will use $s$, $v$, and $f$ to
%range over individual secrets, views, and flips respectively.
We let $X$ range over sets of variables,
and $S,R,M,P,O$$ to range over sets of
secrets, views, and flips (including invocations of the oracle)
respectively. Given a program $\prog$, we write $\iov(\prog)$ to
denote $S \cup V$ where $S$ is the set of secret variables in $\prog$
and $V$ is the set of views in $\prog$, we write $\flips(\prog)$ to
denote the set $F$ of flip variables in $\prog$, and we write
$\vars(\prog)$ to denote $\iov(\prog) \cup \flips(\prog)$. For any set
of variables $X$ and parties $P$, we write $X_P$ to denote the subset
of $X$ owned by any party in $P$, and we write $X_H$ and $X_C$ to
denote the subsets belonging to honest and corrupt parties,
respectively.

@@

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide the random tape and secret inputs to protocols, and record
view assignments. Memories $\store$ are finite (partial) mapping from
variables to binary values $\beta \in \{0,1\}$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto \beta\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = \beta$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store_1 \subseteq \store_2$ iff
$\dom(\store_1) \subseteq \dom(\store_2)$ and $\store_1(x) =
\store_2(x)$ for all $x \in \dom(\store_1)$. We write $\store_1 \cap
\store_2$ to denote the combination of $\store_1$ and $\store_2$
assuming $\store_1(x) = \store_2(x)$ for all $x \in \dom(\store_1)
\cap \dom(\store_2)$, otherwise $\store_1 \cap \store_2$ is undefined.
We write $\store_1 \subseteq \store_2$ iff $\store_1 \cap \store_2
= \store_1$.

Given a set of variables $X$, we write $\store_X$ to denote the
memory $\store$ restricted to the domain $X$, and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$. We let $\stores$ range
over sets of memories with the same domain, and abusing notation
we write $\dom(\stores)$ to denote the common domain,
and $\stores_X \defeq \{ \store_X | \store \in \stores \}$.

Given a variable-free boolean expression $\be$, we write $\cod{\be}$
to denote the standard interpretation of $\be$ in the binary field.
With the introduction of variables to expressions, we have two
concerns. First, we need to interpret variables with respect to a
specific memory, and second, we need to ensure that variables are used
``legally''. That is, since expressions define local computation, all
variables used in an expression must belong to the same client.  Thus,
we denote interpretation of expressions $\be$ possibly containing
variables as $\lcod{\store,\be}{\cid}$, where $\store$ associates
variables with values, and all variables must be owned by client
$\cid$. This is defined in Figure \ref{fig-minifed}.

>>>>

We let $x$ range over \emph{variables}  which are identifiers
where client ownership is specified- e.g., $\elab{\mesg{\mathit{foo}}}{\cid}$
is a message $\mathit{foo}$ that was sent to $\cid$. We let $X$
range over sets of variables, and more specifically, $S$ ranges over sets of secret variables $\elab{\secret{w}}{\cid}$, $R$ ranges over sets of random variables $\elab{\flip{w}}{\cid}$, $M$ ranges over sets of message variables $\elab{\mesg{w}}{\cid}$, $P$ ranges over sets of public variables $\rvl{w}$, and $O$ ranges over sets of output variabels $\out{\cid}$.
Given a program $\prog$, we write $\iov(\prog)$ to
denote the set of $S \cup M \cup P \cup O$ of variables in $\prog$
with ownership made explicit, and we write $\flips(\prog)$ to
denote the set $R$ of random samplings in $\prog$ with ownership
made explicit. We write
$\vars(\prog)$ to denote $\iov(\prog) \cup \flips(\prog)$. For any set
of variables $X$ and parties $P$, we write $X_P$ to denote the subset
of $X$ owned by any party in $P$, in particular we write $X_H$ and $X_C$ to
denote the subsets belonging to honest and corrupt parties,
respectively.

@@

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide the random tape and secret inputs to protocols, and record
view assignments. Memories $\store$ are finite (partial) mapping from
variables to values $v \in \mathbb{Z}_p$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto v\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = v$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store_1 \subseteq \store_2$ iff
$\dom(\store_1) \subseteq \dom(\store_2)$ and $\store_1(x) =
\store_2(x)$ for all $x \in \dom(\store_1)$. We write $\store_1 \cap
\store_2$ to denote the combination of $\store_1$ and $\store_2$
assuming $\store_1(x) = \store_2(x)$ for all $x \in \dom(\store_1)
\cap \dom(\store_2)$, otherwise $\store_1 \cap \store_2$ is undefined.
We write $\store_1 \subseteq \store_2$ iff $\store_1 \cap \store_2
= \store_1$.

Given a set of variables $X$, we write $\store_X$ to denote the
memory $\store$ restricted to the domain $X$, and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$.
%We let $\stores$ range
%over sets of memories with the same domain, and abusing notation
%we write $\dom(\stores)$ to denote the common domain,
%and $\stores_X \defeq \{ \store_X | \store \in \stores \}$.

Given a variable-free boolean expression $\be$, we write $\cod{\be}$
to denote the standard interpretation of $\be$ in the arithmetic field
$\mathbb{Z}{p}$.
With the introduction of variables to expressions, we need to interpret
variables with respect to a specific memory, and all
variables used in an expression must belong to a specified client.  Thus,
we denote interpretation of expressions $\be$ possibly containing
variables as $\lcod{\store,\be}{\cid}$, where $\store$ associates
variables with values, and all variables must be owned by client
$\cid$. This is interpretation is defined in Figure \ref{fig-minifed}.
